Unified Convergence Analysis of FedAve on Non-IID Data

### 2020-04-25 source/sec_theorems.tex
updated result summary
Update sec_theorems.tex

\section{Convergence Results}
This section summarizes the current results and assumptions.
\begin{table}[h!]
\centering
\small
	\begin{tabular}{|c|c|c|c|c|}\hline
		paper         &  Cvx Non-smth & Cvx L-smth & Strongly Cvx Non-smth& Strongly Cvx L-smth \\ \hline
	Accelerated	SGD   &   $\cO(\frac{1}{\sqrt{T}})$     & $\cO(\frac{1}{\sqrt{T}})$   &    $\cO(\frac{1}{T})$   &  $\cO(\frac{1}{T})$    \\\hline
	SGD    &    $\cO(\frac{1}{\sqrt{T}})$  &   $\cO(\frac{1}{\sqrt{NT}})$  &  $\cO(\frac{1}{T})$  & $\cO(\frac{1}{T})$\cite{li2019convergence,haddadpour2019convergence}, $\cO(\frac{1}{NT})$ ours    \\\hline
	\end{tabular}
	\caption{Summarize of related work on federated learning, heterogeneous data.}
\end{table}

>>>>

\section{Convergence Results}
This section summarizes the current results and assumptions.
\begin{table}[h!]
\centering
\small
	\begin{tabular}{|c|c|c|c|c|}\hline
		paper         &  Cvx Non-smth & Cvx L-smth & Strongly Cvx Non-smth& Strongly Cvx L-smth \\ \hline
	Accelerated	SGD   &   $\cO(\frac{1}{\sqrt{T}})$     & $\cO(\frac{1}{\sqrt{T}})$   &    $\cO(\frac{1}{T})$   &  $\cO(\frac{1}{KT})$    \\\hline
	SGD    &    $\cO(\frac{1}{\sqrt{T}})$  &   $\cO(\frac{1}{\sqrt{T}})$  &  $\cO(\frac{1}{T})$  & $\cO(\frac{1}{T})$\cite{li2019convergence,haddadpour2019convergence}, $\cO(\frac{1}{KT})$ ours    \\\hline
	\end{tabular}
	\caption{Summarize of related work on federated learning, heterogeneous data.}
\end{table}

Acceleration of MaSS for linear regression, partial participation $O((1+\frac{4}{K}\cdot(\frac{t}{E}-1))\exp(-\frac{t}{\sqrt{\kappa_{m}\tilde{\kappa}_{m}}}))$
over $O((1+\frac{4}{K}\cdot(\frac{t}{E}-1))\exp(-\frac{t}{\kappa_{m}}))$.
